\documentclass[letterpaper]{article}

\usepackage{hyperref}
\usepackage{geometry}
\usepackage{enumitem}
\usepackage{etaremune}
\usepackage{amssymb}

\usepackage[T1]{fontenc}
\usepackage[sc,osf]{mathpazo}

% Set your name here
\def\name{Wei Yuan}
%math commands
\newcommand{\R}{\mathbb R}


% Replace this with a link to your CV if you like, or set it empty
% (as in \def\footerlink{}) to remove the link in the footer:
% \def\footerlink{http://jblevins.org/projects/cv-template/}

% The following metadata will show up in the PDF properties
\hypersetup{
  colorlinks = true,
  urlcolor = black,
  pdfauthor = {\name},
  pdfkeywords = {mathematics},
  pdftitle = {\name: Curriculum Vitae},
  pdfsubject = {Curriculum Vitae},
  pdfpagemode = UseNone
}

\geometry{
  body={6.5in, 8.5in},
  left=1.0in,
  top=1.25in
}

% Customize page headers
\pagestyle{myheadings}
\markright{\name}
\thispagestyle{empty}

% Custom section fonts
\usepackage{sectsty}
\sectionfont{\rmfamily\mdseries\Large}
\subsectionfont{\rmfamily\mdseries\itshape\large}

% Other possible font commands include:
% \ttfamily for teletype,
% \sffamily for sans serif,
% \bfseries for bold,
% \scshape for small caps,
% \normalsize, \large, \Large, \LARGE sizes.

% Don't indent paragraphs.
\setlength\parindent{0em}

% Make lists without bullets
\renewenvironment{itemize}{
  \begin{list}{}{
    \setlength{\leftmargin}{1.5em}
  }
}{
  \end{list}
}

\begin{document}

% Place name at left
{\huge \name}

% Alternatively, print name centered and bold:
%\centerline{\huge \bf \name}

\vspace{0.25in}

\begin{minipage}{0.60\linewidth}
  \href{http://www.math.ac.cn/}{Institute of Mathematics}\\ 
  \href{http://www.math.ac.cn/}{Academy of Mathematics and Systems Science}\\
   No.55 Zhongguancun East Road, Beijing, China (100190)
\end{minipage}
\begin{minipage}{0.4\linewidth}
  \begin{tabular}{ll}
    Work Phone: & (86-10) 6255-3362 \\
    Mobile Phone: & (86) 13691205628\\
    E-mail: & \href{mailto:wyuan@math.ac.cn}{\tt wyuan@math.ac.cn} \\
  \end{tabular}
\end{minipage}

\section*{Education}
\begin{description}[leftmargin=0.95in, labelwidth=0.9in]
  \item[2003-2009] Ph.D. in Pure Mathematics, University of Chinese Academy of Sciences, Beijing, China.\\
                   Thesis: Kadison-Singer Algebras\\
                   Advisor: Prof. Liming Ge
  \item[2006-2009] Ph.D. in Pure Mathematics, University of New Hampshire, NH, USA.\\
                   Thesis: Kadison-Singer Algebras\\
                   Advisor: Prof. Liming Ge
  \item[1999-2003] B.S. in Mathematics, University of Science and Technology of China.
\end{description}

\section*{Experience}
\begin{description}[labelwidth=0.9in]
  \item[2009-present] Institute of Mathematics AMSS, Assistant Professor.
  \item[2013.8-2013.12] University of New Hampshire, Visiting Scholar.
  \item[2006-2008] University of New Hampshire, Teaching Assistant.
\end{description}

\section*{Fields of Research Interest}
Operator algebras and related topics

\section*{Research}

\subsection*{Published research articles}

\begin{etaremune}
 \item W. Wu and W. Yuan, A remark on central sequence algebras of the tensor product of II$_1$ factors, Proc. Amer. Math. Soc. to appear.

 
 \item W. Wu and W. Yuan, On generators of abelian Kadison-Singer algebras in matrix algebras, Linear Algebra and its Applications, Vol 440, 197-205, 2014.

 \item A. Dong, W. Wu and W. Yuan, On small subspace lattices in Hilbert space, Journal of the Australian Math Society, published online 2013.
 
 \item A. Dong, W. Yuan, C. Hou and G. Chen, Representations and operations on reflexive subspace lattices, Scientia Sinica Mathematica,
         42(4), 321-328, 2012.
   \item C. Hou and W. Yuan, Minimal generating reflexive lattices of projections in finite von Neumann algebras, Math. Ann., 
         Vol 353, Issue 2, 499-517, 2012.
   \item L. Wang and W. Yuan, A new class of Kadison-Singer algebras, Expo. Math., 29, 126-132, 2011.
   \item W. Wu and W. Yuan, The crossed product von Neumann algebras associated with SL$_2(\R)$, Taiwanese Journal of Mathematics, 14(4), 1501-1515, 2010.
   \item L. Ge and W. Yuan, Kadison-Singer Algebras, II: General Case, Proc.Nat.Acad.Sci.U.S.A., Vol 107,no.11, 4840-4844, 2010.
   \item L. Ge and W. Yuan, Kadison-Singer Algebras, Hyperfinite Case, Proc.Nat.Acad.Sci.U.S.A., Vol.107, no.5, 1838-1843, 2010.
   \item W. Wu and W. Yuan, A Note on the Crossed Product of von Neumann Algebras, Acta Mathematica Sinica Chinese Series, 51(4) 803-808, 2008.
\end{etaremune}

    
\subsection*{Work in Progress}
\begin{itemize}
\item B. Fu, L. Ge and W. Yuan, On Sarnak's Conjecture.
\item L. Ge, W. Wu and W. Yuan, On the sphere invariant automorphisms of
finite von Neumann algebras.
\item W. Wu and W. Yuan, On the unbounded operators with trivial
bounded commutant in II$_1$ factors.
\end{itemize}

\section*{Invited Talks at Conferences}
\begin{itemize}
  \item Kadison-Singer Algebras, Operator Algebras and Related Topics, Beijing, July 24, 2010.
\end{itemize}

\section*{Invited Seminar/Colloquium Talks}
\begin{itemize}
    \item Kadison-Singer Algebras
    \begin{itemize}
       \item Qufu Normal University, Department of Mathematics, December 28, 2009.
        \item University of Singapore, Department of Mathematics, May 2, 2009.
     \end{itemize}
    \item On a new class of non selfadjoint algebras
    \begin{itemize}
       \item ChongQing University, Department of Mathematics, September 21, 2011.
     \end{itemize}
 \item Unbounded Operator With Trivial Relative Commutant
     \begin{itemize}
         \item Dartmouth College, Nov. 2, 2013.
     \end{itemize} 
\end{itemize}

\section*{Teaching}
\begin{itemize}
    \item Calculus II (426), University of New Hampshire, Autumn, 2013.
	\item Functional analysis II, University of Chinese Academy of Sciences, Spring
	2011, 2012, 2013.
	\item Introduction to free probability theory(minicourse), East China
	University Of Science And Technology, June, 2009.
\end{itemize}


\section*{Seminars Organized}
\begin{itemize}
  \item Study seminar on operator algebras (with Liguang Wang), QuFu Normal University, July, 2013.
  \item Study seminar on operator algebras and number theory, Institute of
  Mathematics AMSS, Fall 2012-Jan. 2013.
  \item Study seminar on operator algebras(with Liming Ge), Morningside Center
  of Mathematics, 2010, 2011.
  \item Research seminar on operator algebras(with Wenming Wu), Chongqing Normal
  University, October, 2011.
\end{itemize}

\section*{Professional Service}
Refereed articles for research journals:
\begin{itemize}
  \item Expositiones Mathematicae 
  \item Science China Mathematics 
  \item Acta Mathematica Sinica 
  \item Acta Mathematicae Applicatae Sinica
\end{itemize}

\section*{External fundings}
\begin{itemize}
    \item NSFC  
        No.11271390, Group factors and its space theory, 
        Co-Principal Investigator.
    \item NSFC
        No.11301511, On geometric objects in finite factors, 
        Principal Investigator.
    \item NSFC
        No.11371290, KS-algebras and minimal generating 
        lattices of von Neumann algebras, 
        Co-Principal Investigator.
\end{itemize}

\section*{Honors, Awards}
\begin{itemize}
  \item 'Zhong Jia Qing' Mathematics Award 2009.
  \item Outstanding Doctoral Dissertation Award of 
      Chinese Academy of Sciences, 2010.
\end{itemize}

%\section*{Travel History}
%\begin{description}[labelwidth=1.2in]
  %\item[U.S.] 2006, 2007, 2008, 2009
  %\item[SINGAPORE] 2009
  %\item[KOREA(NORTH)] 2011
%\end{description}
\bigskip
% Footer
%\begin{center}
%  \begin{footnotesize}
%    %Last updated: \today \\
%    \href{\footerlink}{\texttt{\footerlink}}
%  \end{footnotesize}
% \end{center}

\end{document}
